A Guide to Designing Experiments to Test Statistical Graphics\thanks{The author(s) received no specific funding for this work.}

### 2025-04-22 index.tex
fix corresponding author thing

%% Author information
\author{Emily
Robinson\footnote{Email: erobin17@calpoly.edu}~\orcidlink{0000-0001-9800-7304}\\{\footnotesize Statistics
Department}, {\footnotesize California Polytechnic State
University}\\Heike
Hofmann\footnote{Email: hhofmann4@unl.edu}~\orcidlink{0000-0001-6216-5183}\\{\footnotesize Statistics
Department}, {\footnotesize University of Nebraska - Lincoln}\\Susan
Vanderplas\footnote{Email: svanderplas2@unl.edu}~\orcidlink{0000-0002-3803-0972}\\{\footnotesize Statistics
Department}, {\footnotesize University of Nebraska - Lincoln}\\}
\begin{document}
\maketitle
\begin{abstract}
In this paper, we discuss considerations and methods for experimentally
testing visualizations. We discuss levels of user engagement with
graphics, common issues when developing a sampling or data generation
model, the importance of pilot testing, and data analysis methods. Along
the way, we also provide recommendations of how to avoid some of the
unique pitfalls of human testing in statistical and visualization
research.
\end{abstract}

>>>>

%% Author information
\author{%
%
Emily Robinson%\footnote{Email: erobin17@calpoly.edu}
~\orcidlink{0000-0001-9800-7304}%
%
\\{\footnotesize Statistics Department}, {\footnotesize California
Polytechnic State University}\\%
Heike Hofmann%\footnote{Email: hhofmann4@unl.edu}
~\orcidlink{0000-0001-6216-5183}%
%
\\{\footnotesize Statistics Department}, {\footnotesize University of
Nebraska - Lincoln}\\%
Susan Vanderplas%\footnote{Email: svanderplas2@unl.edu}
~\orcidlink{0000-0002-3803-0972}%
\footnote{Corresponding author: Susan Vanderplas, svanderplas2@unl.edu}%
\\{\footnotesize Statistics Department}, {\footnotesize University of
Nebraska - Lincoln}\\
}
\begin{document}
\maketitle
\begin{abstract}
In this paper, we discuss considerations and methods for experimentally
testing visualizations. We discuss levels of user engagement with
graphics, common issues when developing a sampling or data generation
model, the importance of pilot testing, and data analysis methods. Along
the way, we also provide recommendations of how to avoid some of the
unique pitfalls of human testing in statistical and visualization
research.
\end{abstract}
